Principles for Open Data Curation: A Case Study with the New York City 311 Service Request Data

### 2024-07-12 manuscript/manuscript.tex
jds style

\documentclass[12pt, titlepage]{article}

\usepackage[margin = 1in]{geometry}
\usepackage{amsmath}
\allowdisplaybreaks
\usepackage{authblk}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}\hypersetup{colorlinks=true, citecolor=blue}
% \usepackage{parskip}
\usepackage{textgreek}
\usepackage{graphicx}
\usepackage{booktabs} % For better looking tables
\usepackage{siunitx} % For alignment of numbers
\usepackage{placeins}
\usepackage{caption}  % For custom captions
\usepackage{float}   % Required for the H specifier
\usepackage{adjustbox}
\usepackage[]{lineno}
\usepackage{comment}
\linenumbers*[1]

%% patches to make lineno work better with amsmath
\newcommand*\patchAmsMathEnvironmentForLineno[1]{%
	\expandafter\let\csname old#1\expandafter\endcsname\csname
	#1\endcsname
	\expandafter\let\csname oldend#1\expandafter\endcsname\csname
	end#1\endcsname
	\renewenvironment{#1}%
	{\linenomath\csname old#1\endcsname}%
	{\csname oldend#1\endcsname\endlinenomath}}%
\newcommand*\patchBothAmsMathEnvironmentsForLineno[1]{%
	\patchAmsMathEnvironmentForLineno{#1}%
	\patchAmsMathEnvironmentForLineno{#1*}}%
\AtBeginDocument{%
	\patchBothAmsMathEnvironmentsForLineno{equation}%
	\patchBothAmsMathEnvironmentsForLineno{align}%
	\patchBothAmsMathEnvironmentsForLineno{flalign}%
	\patchBothAmsMathEnvironmentsForLineno{alignat}%
	\patchBothAmsMathEnvironmentsForLineno{gather}%
	\patchBothAmsMathEnvironmentsForLineno{multline}%
}

\sisetup{
    group-separator = {,},
    round-mode = places,
    round-precision = 2,
    output-decimal-marker = {.},
    table-number-alignment = center,
    table-figures-integer = 6,
    table-figures-decimal = 2,
    table-figures-uncertainty = 2
}

@@

% control floats
\renewcommand\floatpagefraction{.9}
\renewcommand\topfraction{.9}
\renewcommand\bottomfraction{.9}
\renewcommand\textfraction{.2}
\setcounter{totalnumber}{50}
\setcounter{topnumber}{50}
\setcounter{bottomnumber}{50}

@@

\title{Principles for Open Data Curation: A Case Study with the New
York City 311 Service Request Data}

\author[1]{David Tussey}
\author[2]{Jun Yan}
\affil[1]{Former Executive Director, NYC DoITT}
\affil[2]{Department of Statistics, University of Connecticut}

\begin{document}
\maketitle

@@

\bigskip

\noindent
\textit{Keywords:}
	Data cleansing;
	Data Curation;
	Data science;
	NYC Open Data;
	Open data;
	Smart Cities;
	Transparency;
\end{abstract}

\doublespacing

\section{INTRODUCTION} 
\label{sec:intro}
In the early 21st century, the open data movement began 
to take shape, driven by the fundamental belief that 
freely accessible data can transform both societies and 
governments. This movement champions the principles
of transparency, innovation, and public engagement. 
A landmark in this journey was the launch of the United States'
\href{https://www.data.gov}{Data.gov} portal in 2009, a pioneering
platform in making government data widely accessible. Shortly after,
the European Union followed suit, unveiling its
\href{https://data.europa.eu/euodp}{Open Data Portal} in 2012, further
cementing the movement's global reach. Furthermore, the World Bank's Open
Data initiative, initiated in 2010, stands out as a comprehensive
repository for global development data, available at
\href{https://data.worldbank.org}{World Bank Open Data}. 
These initiatives represent significant strides in democratizing data, 
in breaking barriers that once kept valuable information 
on government performance in silos. Their collective impact 
is profound, extending beyond mere data sharing to 
fostering a culture of openness that benefits individuals, 
communities, governments, and economies worldwide 
\citep{barns2016mine, wang2016adoption}.

@@

\begin{figure}[tbp]
 \centering
  \includegraphics[width=0.8\textwidth]{SR_by_Complaint_Type.pdf} 
  \caption{Top 20 complaint\_type(s) and Cumulative Percentage} 
  \label{fig:SR_complaints}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\textwidth]{2-year-trend-SR_closed_by_minute_of_busiest\_day.pdf}
	\caption{SRs Closed Minute-by-Minute on Busiest Day}
	\label{fig:busiestclosed}
\end{figure}

@@

\bibliographystyle{asa}
\bibliography{ref}

>>>>

\documentclass[linenumber]{jdsart}

\volume{0}
\issue{0}
\pubyear{2022}
\articletype{research-article}
\doi{0000}

\usepackage{siunitx} % For alignment of numbers
\sisetup{
    group-separator = {,},
    round-mode = places,
    round-precision = 2,
    output-decimal-marker = {.},
    table-number-alignment = center,
    table-figures-integer = 6,
    table-figures-decimal = 2,
    table-figures-uncertainty = 2
}

@@

@@

\usepackage{comment}
\usepackage{booktabs, textgreek}

\begin{document}

\begin{frontmatter}

\title{Principles for Open Data Curation: A Case Study with the New
York City 311 Service Request Data}
\runtitle{Principles for Open Data Curation}

\author[1]{\inits{D.}\fnms{David}~\snm{Tussey}}
\author[2]{\inits{J.}\fnms{Jun}~\snm{Yan}}
\address[1]{\institution{NYC DoITT}, \cny{USA}}
\address[2]{Department of Statistics,
  \institution{University of Connecticut}, \cny{USA}}

@@

\end{abstract}

\begin{keywords}
  \kwd{Data cleansing}
  \kwd{Data Curation}
  \kwd{Data science}
  \kwd{NYC Open Data}
  \kwd{Open data}
  \kwd{Smart Cities}
  \kwd{Transparency}
\end{keywords}

\end{frontmatter}

\section{INTRODUCTION} 
\label{sec:intro}

In the early 21st century, the open data movement began 
to take shape, driven by the fundamental belief that 
freely accessible data can transform both societies and 
governments. This movement champions the principles
of transparency, innovation, and public engagement. 
A landmark in this journey was the launch of the United States'
\href{https://www.data.gov}{Data.gov} portal in 2009, a pioneering
platform in making government data widely accessible. Shortly after,
the European Union followed suit, unveiling its
\href{https://data.europa.eu/euodp}{Open Data Portal} in 2012, further
cementing the movement's global reach. Furthermore, the World Bank's Open
Data initiative, initiated in 2010, stands out as a comprehensive
repository for global development data, available at
\href{https://data.worldbank.org}{World Bank Open Data}. 
These initiatives represent significant strides in democratizing data, 
in breaking barriers that once kept valuable information 
on government performance in silos. Their collective impact 
is profound, extending beyond mere data sharing to 
fostering a culture of openness that benefits individuals, 
communities, governments, and economies worldwide 
\citep{barns2016mine, wang2016adoption}.

@@

\begin{figure}[tbp]
 \centering
  \includegraphics[width=0.8\textwidth]{SR_by_Complaint_Type.pdf} 
  \caption{Top 20 complaint type(s) and Cumulative Percentage} 
  \label{fig:SR_complaints}
\end{figure}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=\textwidth]{2-year-trend-SR_closed_by_minute_of_busiest_day.pdf}
	\caption{SRs Closed Minute-by-Minute on Busiest Day}
	\label{fig:busiestclosed}
\end{figure}

@@

\bibliographystyle{jds}
\bibliography{ref}
